\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2015-12-30 to-do.tex
add notes on WEC to to-do.tex

>>>>

\vskip.5in
Possible puzzle to explain: WEC has an effect here, and that effect is weakened by the change in EC rules during the Uruguay Round
\begin{itemize}
	\item Read Chad's ``Why Are Safeguards under the WTO So Unpopular?'' (World Trade Review 2002), at \url{C:\Users\Kristy\Dropbox\Research\PE_shocks\Literature\2016}
		\begin{itemize}
			\item Need to understand better what changed, both with safeguard and with other policy instruments
		\end{itemize}
	\item There is this drop off in usage of escape clause (EC) after Uruguay Round (UR) reforms, even though retaliation prohibited for first three years. Why, when retaliation goes \textit{away}?
	\item I'm not sure there's a way to make sense of Ben's point: in my set-up, government doesn't ``get'' something different from lobby than it does directly from the shock. Maybe it should.
		\begin{itemize}
			\item Government feels $\ga$ the same whether it's elevated because of $s$ or because of $e$
			\item What is the neutralizing that happens? Why would the government invoke EC when it knows that WEC is coming anyway? Because it's in another sector where it puts less weight right now?
		\end{itemize}
	\item Need to go to continuous value of EC tariff
		\begin{itemize}
			\item There will be optimal tariff for whatever value of $s$ is realized
				\begin{itemize}
					\item Not sure how fine I want to go with $s$
				\end{itemize}
			\item Lobby will choose its optimal level of $e$. Will this be constrained in any way? Probably not, if there isn't a fixed EC-binding.
		\end{itemize}
\end{itemize}
